\documentclass[letter, 11pt, oneside]{article}
\usepackage{soul} % Used for the title name
\usepackage[compact]{titlesec}
\usepackage{marvosym} % add the symbols for email and phone contact data
\usepackage{fancyhdr} % Required for the footer
\usepackage{tabularx} % Nicer table style than the default


\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

\definecolor{headings}{HTML}{701112} % Dark red color for headings
\definecolor{text1}{HTML}{2b2b2b} % Main document font color, off-black
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
\definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}

\usepackage[none]{hyphenat} % Prevents hyphenation in text


\usepackage[margin=.75in]{geometry}

\linespread{1.05} % Line spacing

% Sections formatting
\titleformat{\section}{\color{headings}
\scshape\large\raggedright}{}{0em}{}[\color{black}\titlerule]

\pagestyle{fancy}

% Prevents overfull hbox and vbox
\hbadness=10000
\hfuzz=50pt
\vbadness=10000
\vfuzz=50pt


% add the symbols for email and phone contact data
\fancyhf{}
\fancyhead[c]{\centering{\renewcommand{\\}{\ {\large\textperiodcentered}\ }}{\Large\Letter} \href{mailto:jcahall@lawschool.gonzaga.edu} {jcahall@lawschool.gonzaga.edu} \ {\Large\Mobilefone} {317.385.2343}} 

\fancyfoot[r]{\scriptsize{\textsuperscript{*}}\footnotesize{The \LaTeX\ source file for this resum\'{e} can be viewed in my \href{https://github.com/josephcahall/prof-docs/blob/master/Joseph\%20Cahall\%20resume.tex} {\underline{GitHub repository}}.}}

\renewcommand\headrulewidth{0pt} % Size of the header rule
\renewcommand\footrulewidth{0.1pt} % Size of the footer rule

\usepackage[pdfborder={0 0 0},bookmarks=true,pdftitle={Joseph Cahall's CV},pdfauthor={Joseph Cahall},pdfsubject={Curriculum Vitae},pdfcreator={https://github.com/josephcahall},pdfproducer={https://github.com/josephcahall}]{hyperref}

%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%%%%%%  NAME AND CONTACT  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\renewcommand{\arraystretch}{1.4}
\begin{tabular}{c}
\color{headings}{\textsc{\Huge{\so{Joseph Cahall}}}}\\ 
\hline
\color{darkmidnightblue}\textbf{\large{\so{Gonzaga University School of Law}}} \\
\end{tabular}}



%%%%%%  EDUCATION  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2012 to 2015} & \textbf{Gonzaga University School of Law, J.D.} \\
 & \textsc{\color{red} GPA} \large{\textbf{\color{red} 3.32} \color{black} Ranked in top $\frac{1} {4}$ of class}
\end{tabularx}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2009 to 2011} & \textsc{\textbf{Washington State University College of Veterinary Medicine,}} \textit{Graduate Program in Neuroscience.}\\ 
\end{tabularx}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2006 to 2009} & \textbf{Indiana University-Purdue University Indianapolis,} \textbf{B.S.,} \textit{Psychology.}\\ 
\end{tabularx}


%%%%%%  LEGAL EXPERIENCE  %%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2013} & \textbf{Summer Extern. \color{blue}Judge Thomas Rice, United States District Court for the Eastern District of  Washington.} Spokane, Wa.\\
My Role & Researched and drafted bench memos for Judge Rice. Topics that I researched included federal jurisdiction, pleading, evidentiary review, and immunity. 
\end{tabularx}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2013 to 2014} & \textbf{Research Assistant. \color{blue}Professor Vickie Williams, Gonzaga University School of Law.} Spokane, Wa.\\
Project &  \href{http://www.slu.edu/Documents/law/SLUJHP/Archives/Vol7-1/Williams_Article.pdf} {Williams, Vickie J., \emph{Life-Sciences Dual Use Research of Concern, Public Health, and the Doctrine of Unconstitutional Conditions} 7(1) \textsc{St. Louis U. J. Health L. \& Policy} 81 (2013)}
\\
My Role & Researched and briefed legal and factual issues related to unconstitutional prior restraint on the publication of scientific research.
\end{tabularx}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2009 to 2011} & \textbf{Research Assistant. \color{blue}Washington State Univeristy Sleep and Performance Research Center} Spokane, Wa.\\
Project & \small{\emph{Local Sleep in the Cerebral Cortex is Modulated by Hemodynamics and Contributes to Cognitive Performance.}} 
\\
My role &  Experimental design \& execution of a 4-day/3-night in-patient sleep study; fabrication and maintenance of EEG \& oximetry equipment for data collection; data analysis in Octave (open-source), C\texttt{++}, SAS\textsuperscript{\tiny{\textregistered}}.
\end{tabularx}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2009} & \textbf{Research Assistant. \color{blue}Washington State University College of Veterinary Medicine.} Pullman, Wa.\\
Project   & \small{\emph{Sleep characteristics of mice expressing the influenza-immunoprotective MX1 gene.}}\\
My role &  Animal neurosurgery; fabrication of electrodes; data analysis in SPSS\textsuperscript{\tiny{\textregistered}}.
\end{tabularx}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2007 to 2009} & \textbf{Research Assistant. \color{blue}Indiana University School of Medicine: Institute of Psychiatric Research.} Indianapolis, In.\\
Project & \small{\emph{Auditory sensory gating and steady-state responses in a rodent model of schizophrenia.}}\\
My role &  Experimental design; animal neurosurgery; fabrication of electrodes \& EEG equipment; data analysis in MATLAB\textsuperscript{\tiny{\textregistered}} \& SPSS\textsuperscript{\tiny{\textregistered}}.
\end{tabularx}



%%%%%%  AWARDS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards and Qualifications} 

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{3cm}X}
\textbf{2014-15}	&  \textbf{Saul Lefkowitz Moot Court Team} Gonzaga University School of Law. \\
\textbf{2014}	&  \textbf{Dean's Honor Roll} Gonzaga University School of Law. \\
\textbf{2013-15}	&  \textbf{Blog \& Social Media Editor} Gonzaga Intellectual Property Law Ass'n. \\
\textbf{2012}    &  \textbf{Winner, ABA Client Counseling Competition} Gonzaga University School of Law. \\
\textbf{2012-15}    &  \textbf{Moot Court Honors Council} Gonzaga University School of Law. \\
%\textbf{2009-10}    &  \textit{Best Creative Writing} IUPUI Literary Journal \& Conf. of Indiana Collegiate Press Ass'n \\ 
%\textbf{2008-09}    &  \textit{Research Fellowship} IUPUI Center for Research \& Learning \\
%\textbf{2007}   &  \textit{Writing Fellowship} \& \textit{Rowland E Smith Award} IUPUI College of Liberal Arts                          
\end{tabularx}


\end{center}

\end{document}
